New_Data_Coherence

### 2019-08-25 Analysis/Coherence_Calculations_New.Rmd
various fixes

# #Repeating for string
# data_dir = "./data/"
# #Read in new string database
# string = read_table2(paste0(data_dir,"9606.protein.links.v11.0.txt.gz"))
# string = string %>% mutate(protein1 = gsub("9606.", "", protein1), 
#                              protein2 = gsub("9606.", "", protein2))
# #Read in ensemble protein ID
# ensembl = biomaRt::useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl", mirror = "www")
# #Get gene set
# genes = biomaRt::getBM(attributes=c('ensembl_peptide_id','hgnc_symbol'), mart = ensembl)
# #Join gene names with string
# string = left_join(string, genes, by = c("protein1" = "ensembl_peptide_id", "protein2" = "ensembl_peptide_id"))
# #Rename to work with our functions
# string = string %>% dplyr::rename(hgnc_symbol_a = hgnc_symbol)
# #Repeat for second set of proteins
# string = left_join(string, genes, by = c("protein2" = "ensembl_peptide_id"))
# string = string %>% dplyr::rename(hgnc_symbol_b = hgnc_symbol)
# string_filt = string %>% filter(combined_score>=500)
# dim(string)
# #Reading in biogrid data
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# #Select human protein-protein interactions
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# #Split based on Biogrid ID system then pull out gene names
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# #Place into matrix in form that disease2frame works on
# links = links %>% mutate(protein1 =protein1, 
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# dim(links)

@@

#       saveRDS(coherence_tab, "coherence_biogrid.rds")
# # Reactome
#       saveRDS(coherence_tab, "coherence_string_react.rds")

@@

@@

disease_select = read_csv("supplementary_table_diseases_selected.csv") %>% dplyr::select(Disease =`Disease name`, `Number of SNPs`, `Number of genes`)

@@

require(writexl)
write_xlsx(coherence_disease, "./tables/supplementary_table_S1.xlsx")

>>>>

```{r}
# #Repeating for string
# 
# data_dir = "./data/"
# 
# #Read in new string database
# 
# string = read_table2(paste0(data_dir,"9606.protein.links.v11.0.txt.gz"))
# 
# string = string %>% mutate(protein1 = gsub("9606.", "", protein1), 
#                              protein2 = gsub("9606.", "", protein2))
# 
# #Read in ensemble protein ID
# 
# ensembl = biomaRt::useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl", mirror = "www")
# 
# #Get gene set
# genes = biomaRt::getBM(attributes=c('ensembl_peptide_id','hgnc_symbol'), mart = ensembl)
# 
# 
# #Join gene names with string
# 
# string = left_join(string, genes, by = c("protein1" = "ensembl_peptide_id", "protein2" = "ensembl_peptide_id"))
# 
# #Rename to work with our functions
# 
# string = string %>% dplyr::rename(hgnc_symbol_a = hgnc_symbol)
# 
# #Repeat for second set of proteins
# 
# string = left_join(string, genes, by = c("protein2" = "ensembl_peptide_id"))
# 
# string = string %>% dplyr::rename(hgnc_symbol_b = hgnc_symbol)
# 
# string_filt = string %>% filter(combined_score>=500)
# 
# dim(string)
# 
```

```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1, 
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)
# 
```

```{r}

@@

```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid.rds")
# }
#   
#   
#
```

# Reactome

```{r}
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_react.rds")
# }
#   
# 
#
```

```{r}

@@

```{r}

@@

disease_select = read_csv("./data/supplementary_table_diseases_selected.csv") %>% dplyr::select(Disease =`Disease name`, `Number of SNPs`, `Number of genes`)

@@

dir.create("../manuscript/tables")
write.csv(coherence_disease, ".././manuscript/tables/supplementary_table_S1.csv", 
          row.names = FALSE)
